Test susieI using chr17 to 22

### 2020-10-02 analysis/simulation-susieI-ukbchr17to22B-gtex.adipose.Rmd
batch susieI

```{r dirs}
simdatadir <- "~/causalTWAS/simulations/simulation_ashtest_20200721/"
outputdir <- "~/causalTWAS/simulations/simulation_susieI_20200813/"
susiedir <- "~/causalTWAS/simulations/simulation_susieI_20200813/"
mrashdir <- "~/causalTWAS/simulations/simulation_ashtest_20200721/"
tag <- '20200813-1-1'
Niter <- 30
```

@@

```{r rpip twas, fig.height=6, fig.width=6}
simtag <- "20200721-1-1"
rpipf <- paste0(simdatadir, simtag, ".pgenerprank.txt")

@@

```{r rpip twas2, fig.height=6, fig.width=6}
rpipf <- paste0(simdatadir, simtag, ".p2rprank.txt")

@@

# Regional BF distribution
mean BF of both SNPs and genes in region as the regional BF.

```{r rBF twas, fig.height=6, fig.width=6}
rpipf <- paste0(simdatadir, simtag, ".rBF.txt")

a <- read.table(rpipf, header = T)
a.c <- a[a$nCausal > 0, ]

par(mfrow=c(2,1))
h1 <- hist(a$rBF, breaks = 5000, xlab = "PIP", main = "regional BF distribution-all", col = "grey", xlim = c(0,10)); grid()
h2 <- hist(a.c$rBF, breaks = h1$breaks, xlab = "PIP", main = "regional BF distribution-causal", col = "salmon",xlim = c(0,10));grid()
```

# MR.ASH regional pip sum distribution

* Use mr.ash for gene only:

```{r rpip 1, fig.height=6, fig.width=6, eval=F}
rpipf <- paste0(simdatadir, simtag, "-mr.ash.mrashrPIP.txt")

a <- read.table(rpipf, header = T)
a.c <- a[a$nCausal > 0, ]
ax <- pretty(0:max(a$rPIP), n = 30)

par(mfrow=c(2,1))
h1 <- hist(a$rPIP, breaks = 100, xlab = "PIP", main = "PIP distribution-all", col = "grey"); grid()
h2 <- hist(a.c$rPIP, breaks = h1$breaks, xlab = "PIP", main = "PIP distribution-causal", col = "salmon");grid()
```

* MR.ash2s for both genes and SNPs using the same data

```{r rpip 2, fig.height=6, fig.width=6}
rpipf <- paste0(simdatadir, simtag, "-mr.ash2s.lassoes-es.mrash2srPIP.txt")

a <- read.table(rpipf, header = T)
a.c <- a[a$nCausal > 0 ,]
ax <- pretty(0:max(a$rPIP), n = 30) # Make a neat vector for the breakpoints

par(mfrow=c(2,1))
h1 <- hist(a$rPIP, breaks = 100, xlab = "PIP", main = "PIP distribution-all", col = "grey"); grid()
h2 <- hist(a.c$rPIP, breaks = h1$breaks, xlab = "PIP", main = "PIP distribution-causal", col = "salmon");grid()
```

@@

## Regions: causal

* Regions: We use regional PIP of both SNP and gene from mr.ash2s > 0.3, and also require at least one causal gene or SNP is present, also, at least one gene.

* Susie run parameters: `L=1`, `null_weight = 0`, didn't update `null_weight` in iterations. We initialize with prior for genes and SNPs as uniform.

```{r param functions}
show_param <- function(mrashfs, susieIfs, susieIfs2){
  param <- do.call(rbind, lapply(mr.ashfs, function(x) t(read.table(x))[2:1,]))

  pars <- cbind(param[seq(1,nrow(param), 2), 2], param[seq(1,nrow(param), 2), 4], param[seq(1,nrow(param), 2), 1], param[seq(2,nrow(param), 2), 1], param[seq(1,nrow(param), 2), 3], param[seq(2,nrow(param), 2), 3])
  colnames(pars) <- c("PVE.gene_truth", "PVE.SNP_truth", paste(rep(c("pi1.gene_", "pi1.SNP_"), each = 2), c("truth", "mr.ash2"), sep = ""))

  param.s <- do.call(rbind, lapply(susieIfs, function(x) {load(x); c(tail(prior.gene_rec, 1), tail(prior.SNP_rec,1))}))

@@

plot_param <- function(df, ...){
  df <- apply(df[ , 2:ncol(df)], 2, function(x) as.numeric(x))
  m <- cbind(df[,"pi1.gene_mr.ash2"], 1:nrow(df), 1 + 1:nrow(df)/nrow(df)/3)
  st <-  cbind(df[,"pi1.gene_susietruth"], 1:nrow(df), 2 + 1:nrow(df)/nrow(df)/3)
  s <- cbind(df[,"pi1.gene_susieI"], 1:nrow(df), 3 + 1:nrow(df)/nrow(df)/3)
  t <- df[1,"pi1.gene_truth"]
  dfp <- rbind(m,st,s)
  plot(dfp[,3], dfp[,1], col = dfp[,2], pch = 19, ylab = "gene pi1", xaxt = "n", xlab="", xlim = c(0.8, 3.5), frame.plot=FALSE, ylim = c(0, max(dfp[,1],t) *1.05), ...)
  axis(side=1, at=1:3, labels = FALSE, tick = F)
  text(x=1:3, 0, labels = c("mr.ash2", "susieI_truth", "susieI"), xpd = T, pos =1)
  abline(h=t, lty = 2, col= "salmon", lwd=1.5)
  grid()

  m <- cbind(df[,"pi1.gene_mr.ash2"]/df[,"pi1.SNP_mr.ash2"], 1:nrow(df), 1 + 1:nrow(df)/nrow(df)/3)
  st <-  cbind(df[,"pi1.gene_susietruth"]/df[,"pi1.SNP_susietruth"], 1:nrow(df), 2 + 1:nrow(df)/nrow(df)/3)
  s <- cbind(df[,"pi1.gene_susieI"]/df[,"pi1.SNP_susieI"], 1:nrow(df), 3 + 1:nrow(df)/nrow(df)/3)
  t <- df[1,"pi1.gene_truth"]/df[1,"pi1.SNP_truth"]
  dfp <- rbind(m,st,s)
  plot(dfp[,3], dfp[,1], col = dfp[,2], pch = 19, ylab = "Enrichment (gene/snp)", xaxt = "n", xlab="", xlim = c(0.8, 3.5),frame.plot=FALSE, ylim = c(0, min(max(dfp[,1],t) *1.05, 150)))
  axis(side=1, at=1:3, labels = FALSE, tick = F)
  text(x=1:3, 0, labels = c("mr.ash2", "susieI_truth", "susieI"), xpd = T, pos =1)
  abline(h= t, lty = 2, col= "darkgreen", lwd=1.5)
  grid()
}

@@

```{r param, fig.height=8, fig.width=6}
tags <- paste(rep(1:3, each = 5), 1:5, sep = "-")
mr.ashfs <- paste0(mrashdir, "20200721-", tags, "-mr.ash2s.lassoes-es.param.txt")
susieIfs <- paste0(outputdir, "20200813-", tags, ".susieIres.Rd")
susieIfs2 <- paste0(outputdir, "20200813-", tags, ".1.txt")

df <- show_param(mrashfs, susieIfs, susieIfs2)
par(mfrow = c(3,2))
plot_param(df[1:5,], main = "1-x: gene.pve ~ 0.01, snp.pve ~ 0.05") 
plot_param(df[6:10,], main = "2-x: gene.pve ~ 0.01, snp.pve ~ 0.05")
plot_param(df[11:15,], main = "3-x: gene.pve ~ 0.01, snp.pve ~ 0.05")
```

```{r pipdist,fig.height=3, fig.width=9}
par(mfrow = c(1,3))
gpip_dist(susieIfs2[1:5], main = "1-x combined")
gpip_dist(susieIfs2[6:10], main = "2-x combined")
gpip_dist(susieIfs2[11:15], main = "3-x combined")
```

## Regions: mrash gene+SNP (1)

* Regions: We use regional PIP of both SNP and gene from mr.ash2s > 0.3.

* Susie run parameters: `L=2`, initialize `null_weight = 0`, update `null_weight` in iterations. We initialize with prior for genes and SNPs as uniform. (We also tried initialize with prior for genes and SNPs as 0.05 and 2.5e-3, results are the same.)

```{r param-6, fig.height=11, fig.width=6}
tags <- paste(rep(1:4, each = 5), 1:5, sep = "-")
mr.ashfs <- paste0(mrashdir, "20200721-", tags, "-mr.ash2s.lassoes-es.param.txt")
susieIfs <- paste0(outputdir, "20200813-", tags, ".config6.susieIres.Rd")
susieIfs2 <- paste0(outputdir, "20200813-", tags, ".config6.susieI.txt")

df <- show_param(mrashfs, susieIfs, susieIfs2)
par(mfrow = c(4,2))
plot_param(df[1:5,], main = "1-x: gene.pve ~ 0.01, snp.pve ~ 0.05")
plot_param(df[6:10,], main = "2-x: gene.pve ~ 0.01, snp.pve ~ 0.05")
plot_param(df[11:15,], main = "3-x: gene.pve ~ 0.01, snp.pve ~ 0.05")
plot_param(df[16:20,], main = "4-x: gene.pve ~ 0.05, snp.pve ~ 0.05")
```
```{r pipdist-6,fig.height=3, fig.width=12}
par(mfrow = c(1,4))
gpip_dist(susieIfs2[1:5], main = "1-x combined")
gpip_dist(susieIfs2[6:10], main = "2-x combined")
gpip_dist(susieIfs2[11:15], main = "3-x combined")
gpip_dist(susieIfs2[16:20], main = "4-x combined")
```

## Regions: mrash gene+SNP (2)

* Regions: We use regional PIP of both SNP and gene from mr.ash2s > 0.3.

* Susie run parameters: `L=2`, `null_weight = 0`. Didn't update `null_weight` in iterations. We initialize with prior for genes and SNPs as uniform.

```{r param-7, fig.height=11, fig.width=6}
tags <- paste(rep(1:4, each = 5), 1:5, sep = "-")
susieIfs <- paste0(outputdir, "20200813-", tags, ".config7.susieIres.Rd")
susieIfs2 <- paste0(outputdir, "20200813-", tags, ".config7.susieI.txt")

df <- show_param(mrashfs, susieIfs, susieIfs2)
par(mfrow = c(4,2))
plot_param(df[1:5,], main = "1-x: gene.pve ~ 0.01, snp.pve ~ 0.05")
plot_param(df[6:10,], main = "2-x: gene.pve ~ 0.01, snp.pve ~ 0.05")
plot_param(df[11:15,], main = "3-x: gene.pve ~ 0.01, snp.pve ~ 0.05")
plot_param(df[16:20,], main = "4-x: gene.pve ~ 0.05, snp.pve ~ 0.05")
```

```{r pipdist-7,fig.height=3, fig.width=12}
par(mfrow = c(1,4))
gpip_dist(susieIfs2[1:5], main = "1-x combined")
gpip_dist(susieIfs2[6:10], main = "2-x combined")
gpip_dist(susieIfs2[11:15], main = "3-x combined")
gpip_dist(susieIfs2[16:20], main = "4-x combined")
```

## Regions: mrash gene only

* Regions: We use regional sum of PIP for genes from mr.ash for genes only > 0.1.

* Susie run parameters: `L=2`. Update `null_weight` in iterations. We initialize with prior for genes and SNPs as uniform, `null_weight = 0`.

```{r param-9, fig.height=11, fig.width=6}
tags <- paste(rep(1:4, each = 5), 1:5, sep = "-")
susieIfs <- paste0(outputdir, "20200813-", tags, ".config9.susieIres.Rd")
susieIfs2 <- paste0(outputdir, "20200813-", tags, ".config9.susieI.txt")

df <- show_param(mrashfs, susieIfs, susieIfs2)
par(mfrow = c(4,2))
plot_param(df[1:5,], main = "1-x: gene.pve ~ 0.01, snp.pve ~ 0.05")
plot_param(df[6:10,], main = "2-x: gene.pve ~ 0.01, snp.pve ~ 0.05")
plot_param(df[11:15,], main = "3-x: gene.pve ~ 0.01, snp.pve ~ 0.05")
plot_param(df[16:20,], main = "4-x: gene.pve ~ 0.05, snp.pve ~ 0.05")
```
```{r pipdist-9,fig.height=3, fig.width=12}
par(mfrow = c(1,4))
gpip_dist(susieIfs2[1:5], main = "1-x combined")
gpip_dist(susieIfs2[6:10], main = "2-x combined")
gpip_dist(susieIfs2[11:15], main = "3-x combined")
gpip_dist(susieIfs2[16:20], main = "4-x combined")
```

## Regions: TWAS gene only

* Regions: We use regional min p value for genes from twas for genes only, requiring this p value in top 5%.

* Susie run parameters: `L=2`. Update `null_weight` in iterations. We initialize with prior for genes and SNPs as uniform, `null_weight = 0`.

```{r param-10, fig.height=11, fig.width=6}
tags <- paste(rep(1:4, each = 5), 1:5, sep = "-")
susieIfs <- paste0(outputdir, "20200813-", tags, ".config10.susieIres.Rd")
susieIfs2 <- paste0(outputdir, "20200813-", tags, ".config10.susieI.txt")

df <- show_param(mrashfs, susieIfs, susieIfs2)
par(mfrow = c(4,2))
plot_param(df[1:5,], main = "1-x: gene.pve ~ 0.01, snp.pve ~ 0.05")
plot_param(df[6:10,], main = "2-x: gene.pve ~ 0.01, snp.pve ~ 0.05")
plot_param(df[11:15,], main = "3-x: gene.pve ~ 0.01, snp.pve ~ 0.05")
plot_param(df[16:20,], main = "4-x: gene.pve ~ 0.05, snp.pve ~ 0.05")
```
```{r pipdist-10,fig.height=3, fig.width=12}
par(mfrow = c(1,4))
gpip_dist(susieIfs2[1:5], main = "1-x combined")
gpip_dist(susieIfs2[6:10], main = "2-x combined")
gpip_dist(susieIfs2[11:15], main = "3-x combined")
gpip_dist(susieIfs2[16:20], main = "4-x combined")
```

## Regions: TWAS gene+SNP top

* Regions: We use regional min p value for genes or SNPs from twas for genes and snps, requiring this p value in top 5% for genes or 1% for SNPs.

* Susie run parameters: `L=2`. Update `null_weight` in iterations. We initialize with prior for genes and SNPs as uniform, `null_weight = 0`.

```{r param-11, fig.height=11, fig.width=6}
tags <- paste(rep(1:4, each = 5), 1:5, sep = "-")
susieIfs <- paste0(outputdir, "20200813-", tags, ".config11.susieIres.Rd")
susieIfs2 <- paste0(outputdir, "20200813-", tags, ".config11.susieI.txt")

df <- show_param(mrashfs, susieIfs, susieIfs2)
par(mfrow = c(4,2))
plot_param(df[1:5,], main = "1-x: gene.pve ~ 0.01, snp.pve ~ 0.05")
plot_param(df[6:10,], main = "2-x: gene.pve ~ 0.01, snp.pve ~ 0.05")
plot_param(df[11:15,], main = "3-x: gene.pve ~ 0.01, snp.pve ~ 0.05")
plot_param(df[16:20,], main = "4-x: gene.pve ~ 0.05, snp.pve ~ 0.05")
```
```{r pipdist-11,fig.height=3, fig.width=12}
par(mfrow = c(1,4))
gpip_dist(susieIfs2[1:5], main = "1-x combined")
gpip_dist(susieIfs2[6:10], main = "2-x combined")
gpip_dist(susieIfs2[11:15], main = "3-x combined")
gpip_dist(susieIfs2[16:20], main = "4-x combined")
```

## Regions: TWAS gene+SNP BF

* Regions: get BF for both genes and SNPs. regional TWAS BF > 2

```{r param 5, fig.height=11, fig.width=6}
tags <- paste(rep(1:4, each = 5), 1:5, sep = "-")
mr.ashfs <- paste0(mrashdir, "20200721-", tags, "-mr.ash2s.lassoes-es.param.txt")
susieIfs <- paste0(outputdir, "20200813-", tags, ".config12.susieIres.Rd")
susieIfs2 <- paste0(outputdir, "20200813-", tags, ".config12.susieI.txt")

df <- show_param(mrashfs, susieIfs, susieIfs2)
par(mfrow = c(4,2))
plot_param(df[1:5,], main = "1-x: gene.pve ~ 0.01, snp.pve ~ 0.05")
plot_param(df[6:10,], main = "2-x: gene.pve ~ 0.01, snp.pve ~ 0.05")
plot_param(df[11:15,], main = "3-x: gene.pve ~ 0.01, snp.pve ~ 0.05")
plot_param(df[16:20,], main = "4-x: gene.pve ~ 0.05, snp.pve ~ 0.05")
```
```{r pipdist-5,fig.height=3, fig.width=12}
par(mfrow = c(1,4))
gpip_dist(susieIfs2[1:5], main = "1-x combined")
gpip_dist(susieIfs2[6:10], main = "2-x combined")
gpip_dist(susieIfs2[11:15], main = "3-x combined")
gpip_dist(susieIfs2[16:20], main = "4-x combined")
```

## Regions: TWAS gene+SNP FDR

* Regions: put gene and SNP pvalues together and get FDR. Seelect regions with minimum FDR < 0.05.

```{r param 13, fig.height=11, fig.width=6}
tags <- paste(rep(1:4, each = 5), 1:5, sep = "-")
mr.ashfs <- paste0(mrashdir, "20200721-", tags, "-mr.ash2s.lassoes-es.param.txt")
susieIfs <- paste0(outputdir, "20200813-", tags, ".config13.susieIres.Rd")
susieIfs2 <- paste0(outputdir, "20200813-", tags, ".config13.susieI.txt")

df <- show_param(mrashfs, susieIfs, susieIfs2)
par(mfrow = c(4,2))
plot_param(df[1:5,], main = "1-x: gene.pve ~ 0.01, snp.pve ~ 0.05")
plot_param(df[6:10,], main = "2-x: gene.pve ~ 0.01, snp.pve ~ 0.05")
plot_param(df[11:15,], main = "3-x: gene.pve ~ 0.01, snp.pve ~ 0.05")
plot_param(df[16:20,], main = "4-x: gene.pve ~ 0.05, snp.pve ~ 0.05")
```
```{r pipdist-13,fig.height=3, fig.width=12}
par(mfrow = c(1,4))
gpip_dist(susieIfs2[1:5], main = "1-x combined")
gpip_dist(susieIfs2[6:10], main = "2-x combined")
gpip_dist(susieIfs2[11:15], main = "3-x combined")
gpip_dist(susieIfs2[16:20], main = "4-x combined")
```

## Regions: all (1)

@@

* Susie run parameters: `L=2`. initialize with `null_weight = 0` and update `null_weight` based on last iteration results. We initialize with prior for genes and SNPs as uniform.

```{r param3, fig.height=11, fig.width=6}
mr.ashfs <- paste0(mrashdir, "20200721-", tags, "-mr.ash2s.lassoes-es.param.txt")
susieIfs <- paste0(outputdir, "20200813-", tags, ".config2.susieIres.Rd")
susieIfs2 <- paste0(outputdir, "20200813-", tags, ".config2.susieI.txt")

df <- show_param(mrashfs, susieIfs, susieIfs2)
par(mfrow = c(4,2))
plot_param(df[1:5,], main = "1-x: gene.pve ~ 0.01, snp.pve ~ 0.05")
plot_param(df[6:10,], main = "2-x: gene.pve ~ 0.01, snp.pve ~ 0.05")
plot_param(df[11:15,], main = "3-x: gene.pve ~ 0.01, snp.pve ~ 0.05")
plot_param(df[16:20,], main = "4-x: gene.pve ~ 0.05, snp.pve ~ 0.05")
```
```{r pipdist-3,fig.height=3, fig.width=12}
par(mfrow = c(1,4))
gpip_dist(susieIfs2[1:5], main = "1-x combined")
gpip_dist(susieIfs2[6:10], main = "2-x combined")
gpip_dist(susieIfs2[11:15], main = "3-x combined")
gpip_dist(susieIfs2[16:20], main = "4-x combined")
```

## Regions: all (2)

* Susie run parameters: `L=1`. Did not update `null_weight` in each iteration. We initialize with prior for genes and SNPs as uniform.

```{r param4, fig.height=11, fig.width=6}
mr.ashfs <- paste0(mrashdir, "20200721-", tags, "-mr.ash2s.lassoes-es.param.txt")
susieIfs <- paste0(outputdir, "20200813-", tags, ".config3.susieIres.Rd")
susieIfs2 <- paste0(outputdir, "20200813-", tags, ".config3.susieI.txt")

df <- show_param(mrashfs, susieIfs, susieIfs2)
par(mfrow = c(4,2))
plot_param(df[1:5,], main = "1-x: gene.pve ~ 0.01, snp.pve ~ 0.05")
plot_param(df[6:10,], main = "2-x: gene.pve ~ 0.01, snp.pve ~ 0.05")
plot_param(df[11:15,], main = "3-x: gene.pve ~ 0.01, snp.pve ~ 0.05")
plot_param(df[16:20,], main = "4-x: gene.pve ~ 0.05, snp.pve ~ 0.05")
```
```{r pipdist-4,fig.height=3, fig.width=12}
par(mfrow = c(1,4))
gpip_dist(susieIfs2[1:5], main = "1-x combined")
gpip_dist(susieIfs2[6:10], main = "2-x combined")
gpip_dist(susieIfs2[11:15], main = "3-x combined")
gpip_dist(susieIfs2[16:20], main = "4-x combined")
```

## Regions: all (others)
* Susie run parameters: `L=1`. initialize with null_weight = 0 and update null_weight based on last iteration results. We initialize with prior for genes and SNPs as uniform. The prior for genes is underestimated for low power settings (1-x, 2-x), many converged to close to 0, for high power settings it is better. 
* Susie run parameters: `L=5`. initialize with null_weight = 0 and update null_weight based on last iteration results. The prior for gene estimation is fine for all runs, however prior for SNPs overestimated about 10 times.
* We have tried different initiation strategies, but the results remain the same.

>>>>

```{r dirs}
simdatadir <- "~/causalTWAS/simulations/simulation_ashtest_20200915/"
outputdir <- "~/causalTWAS/simulations/simulation_susieI_20200915/"
susiedir <- "~/causalTWAS/simulations/simulation_susieI_20200915/"
tag <- '20200915-1-1'
Niter <- 30
```

@@

```{r rpip twas, fig.height=6, fig.width=6}
simtag <- "20200915-1-1"
rpipf <- paste0(outputdir, simtag, ".pgenerprank.txt")

@@

```{r rpip twas2, fig.height=6, fig.width=6}
rpipf <- paste0(outputdir, simtag, ".p2rprank.txt")

@@

@@

```{r param functions}
show_param <- function(phenofs, susieIfs, susieIfs2){
  pars <- do.call(rbind, lapply(phenofs, function(x) {load(read.table(x, header = F, stringsAsFactors = F)[1,1]); 
    c(phenores$param$pve.gene.truth,
      phenores$param$pve.snp.truth,
      length(phenores$param$idx.cgene)/phenores$param$J,
      length(phenores$param$idx.cSNP)/phenores$param$M)}))

  colnames(pars) <- c("PVE.gene_truth", "PVE.SNP_truth", "pi1.gene_truth", "pi1.SNP_truth")

  param.s <- do.call(rbind, lapply(susieIfs, function(x) {load(x); c(tail(prior.gene_rec[prior.gene_rec!=0], 1), tail(prior.SNP_rec[prior.SNP_rec!=0],1))}))

@@

plot_param <- function(df, ...){
  df <- apply(df[ , 2:ncol(df)], 2, function(x) as.numeric(x))
  st <-  cbind(df[,"pi1.gene_susietruth"], 1:nrow(df), 2 + 1:nrow(df)/nrow(df)/3)
  s <- cbind(df[,"pi1.gene_susieI"], 1:nrow(df), 3 + 1:nrow(df)/nrow(df)/3)
  t <- df[1,"pi1.gene_truth"]
  dfp <- rbind(st,s)
  plot(dfp[,3], dfp[,1], col = dfp[,2], pch = 19, ylab = "gene pi1", xaxt = "n", xlab="", xlim = c(0.8, 3.5), frame.plot=FALSE, ylim = c(0, max(dfp[,1],t) *1.05), ...)
  axis(side=1, at=1:2, labels = FALSE, tick = F)
  text(x=1:2, 0, labels = c( "susieI_truth", "susieI"), xpd = T, pos =1)
  abline(h=t, lty = 2, col= "salmon", lwd=1.5)
  grid()

  st <-  cbind(df[,"pi1.gene_susietruth"]/df[,"pi1.SNP_susietruth"], 1:nrow(df), 2 + 1:nrow(df)/nrow(df)/3)
  s <- cbind(df[,"pi1.gene_susieI"]/df[,"pi1.SNP_susieI"], 1:nrow(df), 3 + 1:nrow(df)/nrow(df)/3)
  t <- df[1,"pi1.gene_truth"]/df[1,"pi1.SNP_truth"]
  dfp <- rbind(st,s)
  plot(dfp[,3], dfp[,1], col = dfp[,2], pch = 19, ylab = "Enrichment (gene/snp)", xaxt = "n", xlab="", xlim = c(0.8, 3.5),frame.plot=FALSE, ylim = c(0, min(max(dfp[,1],t) *1.05, 150)))
  axis(side=1, at=1:2, labels = FALSE, tick = F)
  text(x=1:2, 0, labels = c("susieI_truth", "susieI"), xpd = T, pos =1)
  abline(h= t, lty = 2, col= "darkgreen", lwd=1.5)
  grid()
}

@@

## Regions: all

@@

* Susie run parameters: `L=2`. initialize with `null_weight = 0` and update `null_weight` based on last iteration results. We initialize with prior for genes and SNPs as uniform. gene.pve ~ 0.01, snp.pve ~ 0.05.

```{r param1, fig.height=6, fig.width=6}
tags <- paste(rep(1:2, each = 5), 1:5, sep = "-")
phenofs <- paste0(simdatadir, "simu_20200915-", tags, "-pheno.txt")
susieIfs <- paste0(outputdir, "20200915-", tags, ".config1.susieIres.Rd")
susieIfs2 <- paste0(outputdir, "20200915-", tags, ".config1.susieI.txt")

df <- show_param(phenofs, susieIfs, susieIfs2)
par(mfrow = c(2,2))
plot_param(df[1:5,], main = "low power")
plot_param(df[6:10,], main = "high power")
```

```{r pipdist-1,fig.height=3, fig.width=12}
par(mfrow = c(1,2))
gpip_dist(susieIfs2[1:5], main = "low power")
gpip_dist(susieIfs2[6:10], main = "high power")
```
